---
title: "2024 - TCA - Survey - 1"
author: "Niall McGuinness"
format: html
date: "2024-04-11"
---

### Overview
- What survey was conducted?
- When and with whom was it conducted? (date, N (M, F, O))
- How do the participants breakdown in terms of demographic?
(sampling method (random, stratified, cluster, convenience), age, preference)
- Who conducted the survey?
- What was the purpose of the survey?
- How were the results gathered?
- How was user-testing carried out? conditions? (online, in-person, etc.)
- What were the pre-conditions and information provided to the participants?
- How were the results stored?

### Survey Analysis

```{r load the CSV, echo=FALSE}
# Load the data
survey_data <- read.csv("data/survey_data_1_20.csv")
survey_data

```

The survey data generated included 20 rows of respondant data.

```{r summary statistics, echo=FALSE}
median_pl <- median(survey_data$Purchase.Likelihood)
sd_pl <- sd(survey_data$Purchase.Likelihood)

```

The median purchase likelihood score was `r median_pl` with a standard deviation of `r round(sd_pl, 2)`.

```{r}
# Create a histogram of the puchase likelihood
hist(survey_data$Purchase.Likelihood,
     main = "Fig 1.0- Q1: Purchase Likelihood",
     xlab = "Purchase Likelihood",
     ylab = "# Respondants",
     col = "lightblue",
     border = "black")
```

Examining the data in more detail with a QQ plot it is clear that the data is not normally distributed.

```{r}
# Create a QQ plot
qqnorm(survey_data$Purchase.Likelihood)
qqline(survey_data$Purchase.Likelihood)

```

Let's conclude with linear regression to determine correlation between...

```{r}
# Scatterplot
plot(survey_data$Hours.Week, survey_data$Purchase.Likelihood)
```

### Appendix A - Survey Questions

## Game Narrative
1.  **How would you rate the overall game experience? (Numerical)**
    -   Scale: 1 (Poor) to 10 (Excellent)
2.  **How many hours do you play the game per week? (Numerical)**
    -   Open numeric response
3.  **What is your preferred game genre? (Categorical)**
    -   Options: Action, Adventure, Puzzle, Strategy, Other
4.  **On a scale of 1-10, how difficult do you find the game? (Numerical)**
    -   Scale: 1 (Very Easy) to 10 (Very Hard)

## Game Mechanics    
    
5.  **Have you experienced any bugs while playing the game? (Categorical)**
    -   Options: Yes, No
6.  **Which feature of the game do you like the most? (Categorical)**
    -   Options: Graphics, Storyline, Gameplay Mechanics, Multiplayer Mode, Other
7.  **Would you recommend this game to a friend? (Categorical)**
    -   Options: Definitely, Probably, Not Sure, Probably Not, Definitely Not
8.  **How likely are you to purchase in-game content? (Numerical)**
    -   Scale: 0 (Not Likely) to 10 (Very Likely)
    
### Appendix B - Survey Data

A [link](www.dkit.ie) to the survey is provided...


