---
title: "2024 - TCA-3 - Survey"
author: "Dylan Dockery, Ben McQuaile, Luke Cassidy, Emily McCormack"
format: pdf
date: "`r format(Sys.Date(), '%B %d %Y')`"
toc: true
execute:
  echo: false
  warning: false
---

```{r setup}
# install knitr for a pretty table - see Appendix C
if(!require("knitr"))
   install.packages("knitr")
library(knitr)

# install kableExtra for a pretty table - see Appendix D
if(!require("kableExtra"))
   install.packages("kableExtra")
library(kableExtra)
```

## Overview

This is our document detailing the work conducted by our team, VisionWeavers in surveying participants who agreed to take part in testing our game Shades of Solitude.

## Survey Construction

### Categories of Questions

#### Demographics

These survey questions are designed to help understand and segment our audience by characteristics such as age, gender and how much they play games. This helps to inform us make better decisions when designing the game. For example, more experienced gamers might find it easier.

-   **What Gender do you identify as?**

    -   Male
    -   Female
    -   Other

-   **What is your Age Group?**

    -   18-24
    -   25-34
    -   35-44
    -   45-54
    -   55-64
    -   65+

-   **How many hours would you play in games in a given week?**

    -   1-5 Hours
    -   6-15 Hours
    -   16-30 Hours
    -   31-50 Hours
    -   51+ Hours

#### Mechanics

These questions are designed to help us improve the playability and overall enjoyment of our game.

-   **How intuitive did you find the player controls?**
    -   Very intuitive
    -   Somewhat intuitive
    -   Neutral
    -   Somewhat unintuitive
    -   Very unintuitive
-   **Did you experience any difficulties with the player's controls?**
    -   Yes (Please Specify)
    -   No
-   **How challenging did you find the puzzles in the game?**
    -   Too Easy
    -   Just Right
    -   Neutral
    -   Very Difficult
    -   Frustratingly Difficult
-   **Was there a particular puzzle that you felt was too difficult or too easy?**
    -   Too Easy (Please Describe)
    -   Too Difficult (Please Describe)
    -   No

#### Narrative

These questions are designed to help us understand that the themes of our game come across to the player and which elements get these across best. It also helps identify areas that are weak in portraying the theme and need to be improved.

-   **How well do you think the game communicated its theme?**

    -   Very clearly
    -   Somewhat clearly
    -   Neutral
    -   Somewhat unclearly
    -   Very unclear

-   **Which elements of the game helped you understand the theme? (Select all that apply)**

    -   Visuals
    -   Puzzles
    -   Audio
    -   Text/dialogue
    -   Other

#### Audio

These questions help determine the contribution of audio to the game's atmosphere,identifying effective and ineffective elements. Being able to distinguish on effective and ineffective elements help us shape the soundscape of the game to better suit the atmosphere. We can gather insights on how much work is needed on the audio for future releases.

-   **How did you feel about the audio quality and its contribution to the game atmosphere?**

    -   Enhanced the experience greatly
    -   Somewhat enhanced the experience
    -   Did not effect experience
    -   Somewhat detracted from the experience
    -   Greatly detracted from the experience

-   **Were there any audio elements you found particularly effective?**

    -   Yes (Please specify below)
    -   No

-   **Were there any audio elements you found particularly ineffective?**

    -   Yes (Please specify below)
    -   No

#### General

-   **On a scale of 1-10, how likely are you to recommend "Shades of Solitude" to others**

    -   Range 1-10 (Not likely at all to Extremely likely)

## Survey Analysis

```{r load the CSV}
# Load the data
survey_data <- read.csv("data/Customer_Feedback - dylan.csv")
```

The data (N=`r nrow(survey_data)`) was collected from a convenience sample of participants who were asked to complete the survey online. The purpose of the survey was to gather information on a number of categories relating to game mechanic, playabilty, and in-game content.

The results were gathered using Google forms and the data was stored in a CSV file.

## Descriptive Statistics

This section provides basic descriptive statistics for the collected data. It includes measures of central tendency and variability.

### Recommendation Likelihood

The Recommendation Likelihood data was collected on a scale of 0 (Not Likely) to 10 (Very Likely). The data was analyzed to determine the median and standard deviation.

```{r summary statistics}
median_pl <- median(survey_data$Recommendation.Likelihood)
sd_pl <- sd(survey_data$Recommendation.Likelihood)

```

The median Recommendation likelihood score was `r median_pl` with a standard deviation of `r round(sd_pl, 2)`.

```{r histogram likelihood}
# Create a histogram of the Recommendation likelihood
hist(survey_data$Recommendation.Likelihood,
     main = "Fig 1.0 - Q1: Recommendation Likelihood",
     xlab = "Recommendation Likelihood",
     ylab = "# Respondants",
     col = "lightblue",
     border = "darkblue",
     breaks = 6)

```

The histogram in Fig 1.0 shows the distribution of recommendation likelihood scores. The data appears to be left-skewed and unimodal.

```{r boxplot likelihood}
# boxplot of Recommendation likelihood

num_Atmosphere <- as.numeric(
  factor(survey_data$Overall.Atmosphere,
         levels = c("Very engaging", "Somewhat engaging", "neutral", "Somewhat disengaging", "Very disengaging"),
         exclude = NA))

boxplot(survey_data$Recommendation.Likelihood ~ num_Atmosphere,
        survey_data,
        na.action = na.omit,
        col = "lightblue",
        outline = TRUE,
        border = "darkblue",
        horizontal = FALSE,
        main = "Fig 2.0 - Q1: Recommendation Likelihood by Atmosphere",
        xlab = "Overall Atmosphere",
        ylab = "Recommendation Likelihood")


# set how many ticks to put on Y axis
# see Axis Customization - https://r-charts.com/base-r/axes/?utm_content=cmp-true
axis(2, at = c(seq(0, 10, 1)))

```

The boxplot in Fig 2.0 shows the Recommendation Likelihood by Atmosphere. This measures the likelihood of recommending the game based on the atmosphere categories labeled as 1-5 respectively(1 - very engaging, 2 - somewhat engaging)etc. A very engaging(1) atmosphere displayed higher median scores between 8 and 9 with very little variability. A somewhat engaging(2) atmosphere displayed more variability with a lower median around 6 and included an outlier scoring around 3. Somewhat disengaging(4) was represented by a single data point which indicates limited data for this cater gory.

Outlier tells us that the atmosphere was interesting but it might not be something they are massively interested in.

## Tests for Normality(Recommendation)

The Recommendation Likelihood data was tested for normality using a QQ plot and a Shapiro-Wilk test.

```{r normality test 1}

# Create a QQ plot of recommendation likelihood with a title
qqnorm(survey_data$Recommendation.Likelihood,
       main = "Fig 3.0 - Q1: Recommendation Likelihood QQ Plot")
qqline(survey_data$Recommendation.Likelihood)

```

The QQ Plot in Fig 3.0 shows that the data is normally distributed. To confirm this, a Shapiro-Wilk test was conducted.

```{r shapiro test 1}
# Determine normality from shapiro test
results_sw <- shapiro.test(survey_data$Recommendation.Likelihood)
print(results_sw)
#p_value <- results_sw$p.value
#is_normal <- p_value > 0.05


```

A Shapiro Wilk test was conducted on the Recommendation Likelihood data. From the output obtained our Test Statistic(W) was = 0.94, this value was close to 1 which indicates a fairly normal distribution with some deviations. As a result we assume normality and **accept the null hypothesis** as the p-value was 0.24 which was greater than the common alpha level of 0.05.

## Tests for normality(Weekly Playtime)

The Weekly playtime data was tested for normality using a QQ plot and a Shapiro-Wilk test.

```{r normality test 2}
hours_played <- as.numeric(
  factor(survey_data$Weekly.playtime,
         levels = c("1-5hrs", "6-15hrs", "16-30hrs", "31-50hrs", "51+hrs"),
         exclude = NA))


# Create a QQ plot of recommendation likelihood with a title
qqnorm(hours_played,
       main = "Fig 3.1 - Hours Played QQ Plot")
qqline(hours_played)
```

The QQ Plot in Fig 3.1 shows that the data is not normally distributed. To confirm this, a Shapiro-Wilk test was conducted.

```{r shapiro test 2}
# Determine normality from shapiro test
results_sw <- shapiro.test(hours_played)
print(results_sw)
#p_value <- results_sw$p.value
#is_normal <- p_value > 0.05
```

A Shapiro Wilk test was conducted on the Weekly playtime data. From the output obtained our Test Statistic(W) was = 0.86, this value is much lower than 1 which indicates it does not follow normal distribution. As a result we do not assume normality and leads us to **reject the null hypothesis** as the p-value was 0.007156 which was less than the common alpha level of 0.05.

## Tests for Normality(Intuitive Controls)

The QQ Plot in Fig 3.2 shows that the data is normally distributed. To confirm this, a Shapiro-Wilk test was conducted.

```{r normailty test 3}
intuitive_controls <- as.numeric(
  factor(survey_data$Intuitive.Controls,
         levels = c("Very intuitive", "Somewhat intuitive", "Neutral", "Somewhat unintuitive", "Very unintuitive"),
         exclude = NA))

# Create a QQ plot of intuitive_controls with a title
qqnorm(intuitive_controls,
       main = "Fig 3.2 - Intuitive Controls QQ Plot")
qqline(intuitive_controls)

```

The QQ Plot in Fig 3.2 shows that the data is not normally distributed. To confirm this, a Shapiro-Wilk test was conducted.

```{r shapiro test}
# Determine normality from shapiro test
results_sw <- shapiro.test(intuitive_controls)
print(results_sw)
#p_value <- results_sw$p.value
#is_normal <- p_value > 0.05
```

A Shapiro Wilk test was conducted on the Weekly playtime data. From the output obtained our Test Statistic(W) was = 0.71, this value is much lower than 1 which indicates it does not follow normal distribution. As a result we do not assume normality and leads us to **reject the null hypothesis** as the p-value was 0.000005 which was less than the common alpha level of 0.05.

## Correlation Analysis

### Hours per week vs Reccomendation Likelihood (Numerical)

This section investigates the relationships between two paired numerical variables. Both numerical variables were examined for normality. While Recommendation Likelihood was considered normal, Hours per week was not. However we stilled use Pearson's correlation coefficient to assess the strength of the relationship between these numerical variables.

```{r correlation analysis}
# Scatterplot
plot(hours_played, survey_data$Recommendation.Likelihood,
     main = "Fig 4.0 - Q2: Hours per Week vs Recommendation Likelihood",
     xlab = "Hours per Week",
     ylab = "Recommendation Likelihood",
     xaxt = "n")
axis(1, at = hours_played, labels = survey_data$Weekly.playtime, las = 1) 

points(hours_played, survey_data$Recommendation.Likelihood)

```

The scatterplot above shows the relationship between the number of hours played per week and the likelihood of recommending the game. The data points are spread across the plot, indicating a potential relationship between the two variables.

```{r pearson correlation test}
# linear correlation hours played vs recommendation likelihood using spearman
cor_results <- cor.test(hours_played, survey_data$Recommendation.Likelihood, method = "pearson")
```

```{r correlation output 1}
# output results for linear correlation
cor_results
```

A correlation test between the number of hours played per week and the likelihood of recommending the game was conducted. The results of the correlation test indicate a `r if(cor_results$p.value < 0.05){"significant"}else{"non-significant"}` relationship between the number of hours played per week and the likelihood of purchasing in-game content. The estimated correlation is `r round(cor_results$estimate,2)`.

Based on these results, there is no substantial evidence to conclude that there is a meaningful or statistically significant correlation between the number of hours played and the likelihood of recommending the product.

### Hours Played vs Controls Intuitiveness (Catergorical)

In this section, we will examine the relationship between how intuitive the controls were and amount of hours people play games in a week . We will convert the categorical data to numerical data(done above) and then calculate the correlation between the two variables. Both numerical variables were examined for normality and are considered not normal. However we still used Spearman's correlation coefficient to assess the strength of the relationship between these categorical variables.

```         
```

```{r scatterplot}
# plot linear correlation hours_played vs intuitive controls
plot(hours_played,intuitive_controls,
     main = "Fig 4.0 - Q3: Hours played vs intuitive controls",
     xlab = "Hours Played",
     ylab = "Intuitive controls",
     xaxt = "n")
axis(1, at = hours_played, labels = survey_data$Weekly.playtime, las = 1) 
points(hours_played, intuitive_controls)
```

The scatterplot above shows the relationship between hours played and the intuitiveness of the controls. The data points are spread across the plot, indicating a potential relationship between the two variables.

```{r spearman correlation test}
# linear correlation hours played vs intuitive controls using spearman
cor_results <- cor.test(hours_played, intuitive_controls,
                        method = "spearman",exact=FALSE)
```

```{r correlation output 2}
# output results for linear correlation
cor_results

```

A correlation test between the hours played and the intuitiveness of the controls to was conducted. The results of the correlation test indicate a `r if(cor_results$p.value < 0.05){"significant"}else{"non-significant"}` relationship between the hours played and the likelihood of recommending the game to a friend. The estimated correlation is `r round(cor_results$estimate,2)`.

The Spearman's rank correlation test shows a significant moderate negative correlation between the hours played and the ratings of intuitive controls. This could mean that players who spend more hours playing rate the controls as more intuitive. This is due to the labeling, for example( 1 - hours played = 1-5hrs and 1 - Intuitive controls = Very intuitive)

## Appendix A - Tables

### Categorical to Numerical

Table 1.0 below shows the results of converting the categorical data to numerical data for the hours played and controls

```{r table and plot, echo=FALSE}
table_cat_to_num <- data.frame(hours_played,intuitive_controls)

kable(table_cat_to_num, caption = "Table 1.0 - Categorical to Numerical Conversion",
      col.names = c("Weekly Playtime", "Intuitive Controls"))
```

## Appendix B - Survey Data

Table 2.0 below shows the raw survey data collected from the participants.

```{r survey data, echo=FALSE}

kable(survey_data, 
      caption = "Raw Survey Data")

```
