---
title: "TCA-3 Survey"
author: "Ben McQuaile, Dylan Dockery, Luke Cassidy, Emily McCormack"
format: pdf
---

## Overview

This is our document detailing the work conducted by our team, VisionWeavers in surveying participants who agreed to take part in testing our game Shades of Solitude.

## Survey Construction

### Categories

#### Demographics

-   **What Gender do you identify as?**

    -   Male
    -   Female
    -   Other

-   **What is your Age Group?**

    -   18-24
    -   25-34
    -   35-44
    -   45-54
    -   55-64
    -   65+

-   **How many hours would you play in games in a given week?**

    -   1-5 Hours
    -   6-15 Hours
    -   16-30 Hours
    -   31-50 Hours
    -   51+ Hours

#### Mechanics

-   **How intuitive did you find the player controls?**
    -   Very intuitive
    -   Somewhat intuitive
    -   Neutral
    -   Somewhat unintuitive
    -   Very unintuitive
-   **Did you experience any difficulties with the player's controls?**
    -   Yes (Please Specify)
    -   No
-   **How challenging did you find the puzzles in the game?**
    -   Too Easy
    -   Just Right
    -   Neutral
    -   Very Difficult
    -   Frustratingly Difficult
-   **Was there a particular puzzle that you felt was too difficult or too easy?**
    -   Too Easy (Please Describe)
    -   Too Difficult (Please Describe)
    -   No

#### Narrative

#### Visuals

#### Audio

### Survey Analysis

The data (N=`r nrow(survey_data)`) was collected from a convenience sample of participants who were asked to complete the survey online. The purpose of the survey was to gather information on a number of categories relating to game mechanics, visuals, audio and narrative.

## Running Code

When you click the **Render** button a document will be generated that includes both content and the output of embedded code. You can embed code like this:

```{r}
1 + 1
```

You can add options to executable code like this

```{r}
#| echo: false
2 * 2
```

The `echo: false` option disables the printing of code (only output is displayed).
